---
title: "Analysis Code - Study 1 and 2"
author: "Kate Schertz"
date: "8/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Box Sync/Documents/MyOngoing/ThoughtContent_Abstract/ForcedChoice/")

library(tidyverse)
library(lme4)
library(ggplot2)
library(stargazer)
```

#Data Setup Study 1
```{r}

testnsed <- read_csv("TestingNSED_AllTopicData (Manuscript Study 1).csv")

nsed_longer <- testnsed %>% pivot_longer(cols=-Subject, names_to = "Image", values_to = "Topic")
nsed_longer$Topic <- as.factor(nsed_longer$Topic)
nsed_longer$Image <- as.factor(nsed_longer$Image)
nsed_longer$Subject <- as.factor(nsed_longer$Subject)

nsed_low_imgs <- colnames(testnsed)[2:21]
nsed_high_imgs <- colnames(testnsed)[22:41]

#Adding which NSED condition each image belongs to
nsed_longer <- nsed_longer %>% 
  mutate(NSED = case_when(
    Image %in% nsed_low_imgs ~ "Low",
    Image %in% nsed_high_imgs ~ "High"
  ))

nsed_longer$NSED <- factor(nsed_longer$NSED, levels = c("Low","High"))

#Creating individual columns for each topic in order to perform logistic regression
nsed_longer <- nsed_longer %>% 
  mutate(Art = if_else(Topic == "Art", 1, 0),
         Celebration = if_else(Topic == "Celebration",1,0),
         Family = if_else(Topic == "Family",1,0),
         LifeEmotion = if_else(Topic == "Life&Emotion",1,0),
         Nature = if_else(Topic == "Nature", 1, 0),
         Park = if_else(Topic == "Park", 1, 0),
         Religion = if_else(Topic == "Religion", 1, 0),
         SLJ = if_else(Topic == "Spiritual&LifeJourney", 1, 0),
         TimeMemories = if_else(Topic == "Time&Memories", 1, 0),
         WorldPeace = if_else(Topic == "World&Peace", 1, 0))
```

#Study 1 - Main Analysis
```{r}
#Model for predicting Spiritual & Life Journey topic
slj_nsed_model <- glmer(SLJ ~ NSED + (1 | Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"), nAGQ = 1)
summary(slj_nsed_model)

slj_nsed_nullmodel <- glmer(SLJ ~ 1 + (1 | Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"), nAGQ = 1)
summary(slj_nsed_nullmodel)

anova(slj_nsed_model, slj_nsed_nullmodel)

# Odds Ratio. 1.5 times as likely to be chosen in High NSED. In original study with intact images, the odds ratio was 1.6.
exp(slj_nsed_model@beta[2])

#Model for predicting Nature topic
nat_nsed_nullmodel <- glmer(Nature ~ 1 + (1 | Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"), nAGQ = 1)

nat_nsed_model <- glmer(Nature ~ NSED + (1 | Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"), nAGQ = 1)

# Comparing models. Does not match predictions - Not significant. In original model beta = .50
summary(nat_nsed_nullmodel)
summary(nat_nsed_model)
anova(nat_nsed_model, nat_nsed_nullmodel)

#Nicer table output
stargazer(slj_nsed_model, nat_nsed_model, ci=TRUE, single.row = TRUE, type = "text", intercept.bottom = FALSE, intercept.top = TRUE, align = TRUE)
```

#Data Setup Study 2
```{r}

testnat <- read_csv("TestingNaturalness_AllTopicData (Manuscript Study 2).csv")

nat_longer <- testnat %>% pivot_longer(cols=-Subject, names_to = "Image", values_to = "Topic")
nat_longer$Topic <- as.factor(nat_longer$Topic)
nat_longer$Image <- as.factor(nat_longer$Image)
nat_longer$Subject <- as.factor(nat_longer$Subject)

nat_low_imgs <- colnames(testnat)[2:21]
nat_high_imgs <- colnames(testnat)[22:41]

#Adding which NSED condition each image belongs to
nat_longer <- nat_longer %>% 
  mutate(Naturalness = case_when(
    Image %in% nat_low_imgs ~ "Low",
    Image %in% nat_high_imgs ~ "High"
  ))

nat_longer$Naturalness <- factor(nat_longer$Naturalness, levels = c("Low","High"))

#Creating individual columns for each topic in order to perform logistic regression
nat_longer <- nat_longer %>% 
  mutate(Art = if_else(Topic == "Art", 1, 0),
         Celebration = if_else(Topic == "Celebration",1,0),
         Family = if_else(Topic == "Family",1,0),
         LifeEmotion = if_else(Topic == "Life&Emotion",1,0),
         Nature = if_else(Topic == "Nature", 1, 0),
         Park = if_else(Topic == "Park", 1, 0),
         Religion = if_else(Topic == "Religion", 1, 0),
         SLJ = if_else(Topic == "Spiritual&LifeJourney", 1, 0),
         TimeMemories = if_else(Topic == "Time&Memories", 1, 0),
         WorldPeace = if_else(Topic == "World&Peace", 1, 0))
```

#Study 2 - Main Analysis
```{r}
#Model for Spiritual & Life Journey topic
slj_nat_model <- glmer(SLJ ~ Naturalness + (1 | Subject) + (1|Image), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"), nAGQ = 1)
summary(slj_nat_model)

slj_nat_nullmodel <- glmer(SLJ ~ 1 + (1 | Subject) + (1|Image), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"), nAGQ = 1)
summary(slj_nat_nullmodel)

# Comparing the models. Results are as expected. Negative effect of naturalness on choosing SLJ.
anova(slj_nat_model, slj_nat_nullmodel)

# Odds ratio. 2.4 times as likely to be chosen in Low Naturalness. In original paper, was 1.3.
exp(-slj_nat_model@beta[2])

#Model predicting nature topic
nat_nat_model <- glmer(Nature ~ Naturalness + (1 | Subject) + (1|Image), data = nat_nat_melt, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"), nAGQ = 1)
summary(nat_nat_model)

nat_nat_nullmodel <- glmer(Nature ~ 1 + (1 | Subject), data = nat_nat_melt, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"), nAGQ = 10)
summary(nat_nat_nullmodel)

# Comparing models. Results are as predicted and much stronger effect than in original
anova(nat_nat_model, nat_nat_nullmodel)

# Odds ratio. Nature 3.7 times as likely to chosen in high Naturalness condition, in original OR = 2.0
exp(nat_nat_model@beta[2])

stargazer(slj_nat_model, nat_nat_model, ci=TRUE, single.row = TRUE, type = "text", intercept.bottom = FALSE, intercept.top = TRUE, align = TRUE)
```

#Study 1 - Supplemental Analysis
Supplemental analyses include logistic regressions for all other topics (i.e. Not Spiritual & Life Journey and Nature), and logistic regression for Spiritual & Life Journey and Nature for a smaller image set (17 images per group instead of 20 per group) with no statisticial difference in naturalness ratings. For models that resulted in sigular fit with both random intercepts, changed model to only subject as random intercept.
```{r}
#NSED models with adjusted image set (not statistically significant naturalness ratings between the two image groups). Images were identified previously - removing lowest three rated images from NL group and highest three rated images from NH group.

img_to_remove <- c("NL05","NL15","NL17","NH11","NH15","NH19")
nsed_longer_natmatched <- nsed_longer %>% filter(!(Image %in% img_to_remove))

#Spiritual & Life Journey Model
slj_nsed_model_natmatched <- glmer(SLJ ~ NSED + (1 | Subject) + (1|Image), data = nsed_longer_natmatched, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"), nAGQ = 1)
summary(slj_nsed_model_natmatched)

slj_nsed_nullmodel_natmatched <- glmer(SLJ ~ 1 + (1 | Subject) + (1|Image), data = nsed_longer_natmatched, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"), nAGQ = 1)
summary(slj_nsed_nullmodel_natmatched)

anova(slj_nsed_model_natmatched, slj_nsed_nullmodel_natmatched)

#Nature Model
nat_nsed_nullmodel_natmatched <- glmer(Nature ~ 1 + (1 | Subject) + (1|Image), data = nsed_longer_natmatched, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"), nAGQ = 1)
summary(nat_nsed_model_natmatched)

nat_nsed_model_natmatched <- glmer(Nature ~ NSED + (1 | Subject) + (1|Image), data = nsed_longer_natmatched, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"), nAGQ = 1)
summary(nat_nsed_nullmodel_natmatched)

anova(nat_nsed_model_natmatched, nat_nsed_nullmodel_natmatched)


#NSED Models for all topics. Nothing is significant. With intact images, NSED had a significant effect on LifeEmotions (pos), Park (neg), and Religion (pos)
#Art
art_nsed_model <- glmer(Art ~ NSED + (1 | Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(art_nsed_model)
art_nsed_nullmodel <- glmer(Art ~ 1 + (1 | Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(art_nsed_model, art_nsed_nullmodel)
#Celebration
cel_nsed_model <- glmer(Celebration ~ NSED + (1 | Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(cel_nsed_model)
cel_nsed_nullmodel <- glmer(Celebration ~ 1 + (1 | Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(cel_nsed_model, cel_nsed_nullmodel)
#Family
fam_nsed_model <- glmer(Family ~ NSED + (1 | Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(fam_nsed_model)
fam_nsed_nullmodel <- glmer(Family ~ 1 + (1 | Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(fam_nsed_model, fam_nsed_nullmodel)
#LifeEmotion
le_nsed_model <- glmer(LifeEmotion ~ NSED + (1 | Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(le_nsed_model)
le_nsed_model2 <- glmer(LifeEmotion ~ NSED + (1 | Subject), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(le_nsed_model2)
le_nsed_nullmodel <- glmer(LifeEmotion ~ 1 + (1 | Subject), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(le_nsed_model2, le_nsed_nullmodel)
#Park
park_nsed_model <- glmer(Park ~ NSED + (1 | Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(park_nsed_model)
park_nsed_model2 <- glmer(Park ~ NSED + (1 | Subject), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(park_nsed_model2)
park_nsed_nullmodel <- glmer(Park ~ 1 + (1 | Subject), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(park_nsed_model2, park_nsed_nullmodel)
#Religion
rel_nsed_model <- glmer(Religion ~ NSED + (1|Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(rel_nsed_model)
rel_nsed_model2 <- glmer(Religion ~ NSED + (1|Subject), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(rel_nsed_model)
rel_nsed_nullmodel <- glmer(Religion ~ 1 + (1 | Subject), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(rel_nsed_model2, rel_nsed_nullmodel)
#TimeMemories
time_nsed_model <- glmer(TimeMemories ~ NSED + (1 | Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(time_nsed_model)
time_nsed_nullmodel <- glmer(TimeMemories ~ 1 + (1 | Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(time_nsed_model, time_nsed_nullmodel)
#WorldPeace
world_nsed_model <- glmer(WorldPeace ~ NSED + (1 | Subject) + (1|Image), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(world_nsed_model)
world_nsed_model2 <- glmer(WorldPeace ~ NSED + (1 | Subject), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(world_nsed_model2)
world_nsed_nullmodel <- glmer(WorldPeace ~ 1 + (1 | Subject), data = nsed_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(world_nsed_model2, world_nsed_nullmodel)
```


#Study 2 - Supplemental Analysis
Supplemental analyses include logistic regressions for all other topics (i.e. Not Spiritual & Life Journey and Nature). For models that resulted in sigular fit with both random intercepts, changed model to only subject as random intercept.
```{r}
#Naturalness models for all topics. With intact images, significant predictor of TimeMemories (pos), WorldPeace (neg), Family (neg), Park (pos), Art (neg), Religion (pos). Here Celebration (neg), Religion (pos), TimeMemories (neg) are significant
#Art. NS
art_nat_model <- glmer(Art ~ Naturalness + (1 | Subject) + (1|Image), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(art_nat_model)
art_nat_model2 <- glmer(Art ~ Naturalness + (1 | Subject), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(art_nat_model2)
art_nat_nullmodel <- glmer(Art ~ 1 + (1 | Subject), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(art_nat_model2, art_nat_nullmodel)
#Celebration. Significant - negative
cel_nat_model <- glmer(Celebration ~ Naturalness + (1 | Subject) + (1|Image), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(cel_nat_model)
cel_nat_model2 <- glmer(Celebration ~ Naturalness + (1 | Subject), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(cel_nat_model2)
cel_nat_nullmodel <- glmer(Celebration ~ 1 + (1 | Subject), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(cel_nat_model2, cel_nat_nullmodel)
#Family
fam_nat_model <- glmer(Family ~ Naturalness + (1 | Subject) + (1|Image), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(fam_nat_model)
fam_nat_model2 <- glmer(Family ~ Naturalness + (1 | Subject), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(fam_nat_model2)
fam_nat_nullmodel <- glmer(Family ~ 1 + (1 | Subject), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(fam_nat_model2, fam_nat_nullmodel)
#LifeEmotion
le_nat_model <- glmer(LifeEmotion ~ Naturalness + (1 | Subject) + (1|Image), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(le_nat_model)
le_nat_nullmodel <- glmer(LifeEmotion ~ 1 + (1 | Subject) + (1|Image), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(le_nat_model, le_nat_nullmodel)
#Park
park_nat_model <- glmer(Park ~ Naturalness + (1 | Subject) + (1|Image), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(park_nat_model)
park_nat_nullmodel <- glmer(Park ~ 1 + (1 | Subject) + (1|Image), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(park_nat_model, park_nat_nullmodel)
#Religion. Significant - positive
rel_nat_model <- glmer(Religion ~ Naturalness + (1 | Subject) + (1|Image), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(rel_nat_model)
rel_nat_nullmodel <- glmer(Religion ~ 1 + (1 | Subject) + (1|Image), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(rel_nat_model, rel_nat_nullmodel)
#TimeMemories. Significant - negative
time_nat_model <- glmer(TimeMemories ~ Naturalness + (1 | Subject) + (1|Image), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(time_nat_model)
time_nat_nullmodel <- glmer(TimeMemories ~ 1 + (1 | Subject) + (1|Image), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(time_nat_model, time_nat_nullmodel)
#WorldPeace
world_nat_model <- glmer(WorldPeace ~ Naturalness + (1 | Subject) + (1|Image), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
summary(world_nat_model)
world_nat_nullmodel <- glmer(WorldPeace ~ 1 + (1 | Subject) + (1|Image), data = nat_longer, family = binomial(logit), control = glmerControl(optimizer = "bobyqa"))
anova(world_nat_model, world_nat_nullmodel)
```

